\documentclass[11pt, a4paper]{article}

\usepackage{times}

\usepackage{ifthen}

\usepackage{amsmath}

\usepackage{amssymb}

\usepackage{graphicx}

\usepackage{setspace}



%%% page parameters

\oddsidemargin -0.5 cm

\evensidemargin -0.5 cm

\textwidth 15 cm

\topmargin -1.2 cm

\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize

\setlength{\parskip}{0pt}



\begin{document}



%%%mention the no, time, and venue of the meeting

\noindent The week 6 Software Engineering Group (PG4) Project weekly meeting will be held in {\bf Room 4.62 (Ingkarni Wardli)} at {\bf 10:40am on Tuesday 30th August 2016}.



\vspace*{15pt}

\begin{center}

\huge \bf Agenda

\end{center}



%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.

\section*{Chair: Liang Yuan}

\vspace*{10pt}



%%%if some students cannot make the meeting due to some reasons, their names should appear here.

\section{Apologies}

\begin{itemize}

\item none

\end{itemize}



%%%short presentation about the work of previous week or any milestone specified in the course.

\section{Present}

\begin{itemize}

\item Tao Zhang

\item Yi Lin

\item Yuan Liang

\item Lili Wu

\item Zeqi Fu

\item Navdeep Singh

\item Yann Frizenschaf

\end{itemize}



%%%any schedules for this meeting should go next, each with a separate section.

%%%for example, the first meeting is about requirement elicitation, like the following.

\section{Work Progress}

Liang Yuan will briefly describe progress of the project since the previous meeting, including:

\begin{enumerate}

\item SRS draft is completed.
 
\item SMSP draft will be finished this week.

\item Basic movement is completed.

\item Basic obstacle avoidance is completed.

\item GUI has been updated.

\end{enumerate}

\section{GUI Update}

We use java swing to build GUI, according to client requirement last meeting. We updated GUI, including the bigger button and redesign the layout of the button.

\section{Movement Demo}

We will show the basic movement of the robot that we have done:

\begin{enumerate}

\item Using "forward", "backward", "right", "left" button to control the robot to move forward, backward, and turn right, turn left.

\item The robot can detect obstacle. When obstacle is detected, the robot will turn right, and measure the length of the obstacle.

\item The forward function will be updated.

\item The emergency stop button will be added soon.

\item The close button to close the sensors.

\end{enumerate}
 
 

%%%more issues should make it like the above one.

\section{Other Issues}

NIL

%%%finally, specifies time of next meeting

\vspace*{10pt}

\noindent The next meeting is to be held in {\bf Room 4.62 (Ingkarni Wardli)} at {\bf 10:40am on Tuesday 6th September 2016}.





\end{document}