\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm
\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}

\begin{document}


\vspace*{15pt}
\begin{center}
\huge \bf Meeting Minutes
\end{center}

\section*{Chair: Liang Yuan}
\vspace*{10pt}

\section{Date and Time}
\begin{itemize}
\item Date: 30/08/2016
\item Time: 10:40am - 11:00am
\end{itemize}

\section{Apologies}
\begin{itemize}
\item none
\end{itemize}

\section{Present}
\begin{itemize}
\item Tao Zhang
\item Yi Lin
\item Yuan Liang
\item Lili Wu
\item Zeqi Fu
\item Navdeep Singh
\item Yann Frizenschaf
\end{itemize}

\section{Secretary}
\begin{itemize}
\item Lili Wu
\end{itemize}

\section{Summary }
Liang Yuan summarized the progress of the project:

\begin{enumerate}
\item SRS draft is completed based on clarification of requirements.
\item The SPMP draft is planned to be finished in this week.
\item Basic movement is completed.
\item Basic obstacle avoidance is completed.
\item GUI is updated in accordance with requirements from the requirements of the client in the meeting last week.
\end{enumerate}

\section{Presentation of movements by Tao and Yann}

\begin{itemize}
\item Movements of turning to four sides.
\item Obstacle detecting and avoidance by turning right manually.
\end{itemize}

\section{GUI fixed and presentation by Yann}

\begin{itemize}
\item Redesigned GUI is shown and updated buttons are operated by keyboard.
\end{itemize}

\section{Other Issues}
\begin{itemize}
\item Milestones of releases could be set by ourselves.
\item Unit testing and integration testing cases documentation could not be shown until final presentation.
\item Sensor design and configuration should be changed a little bit.
\item Light sensor map-surveying would be commences based on DTD release this week.
\end{itemize}

\vspace*{10pt}
\noindent Note: Next client meeting to be held on 6 September 2016.


\end{document}
