\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[english,ngerman]{babel}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm
\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}

\begin{document}


\vspace*{15pt}
\begin{center}
\huge \bf Meeting Minutes
\end{center}

\section*{Chair: Tao Zhang}
\section*{Secretory: Yi Lin}
\vspace*{10pt}

\section{Date and Time}
\begin{itemize}
\item Date: 4/10/2016
\item Time: 10:40am - 11:00am
\end{itemize}

\section{Apologies}
\begin{itemize}
\item noon
\end{itemize}

\section{Present}
\begin{itemize}
\item Tao Zhang
\item Yi Lin
\item Yuan Liang
\item Lili Wu
\item Zeqi Fu
\item Navdeep Singh
\item Yann Frizenschaf
\end{itemize}



\section{Summary }
\subsection{Code improvement}
Tao Zhang summarized  the improvement  of the system.
 
\begin{itemize}
\item New function of navigation
\item The map is shown on the GUI in real time.
\item The plan will update the function of saving map.
\item Milestone 2 Demo.
\item Some Discontinuities in the Boundary.
\item Bug of stop at the boundary, avoid barrier, and the extra number on the may.
\end{itemize}

\subsection{SDD}
Yann Frizenschaf summarized of the SDD progress.
\begin{itemize}
\item Almost completed the SDD draft.
\end{itemize}

\subsection{Testing}
Zeqi Fu summarized of the testing plan.
\begin{itemize}
\item The testing job will use modularization.
\end{itemize}



\section{Milestone 2 Freeze}
\begin{itemize}
\item Show Mapping function on a GUI

\end{itemize}
\section{Feedback}
\begin{itemize}
\item The backward should be hidden at the final demonstration.
\item The map is not precise.
\item Update the "saving map" function.
\item GUI testing use special tools by automatically.
\item If the provided map does not work at the final demonstration, we could use ourself map.
\item The page number should fix in the SPMP.
\item The revision history should change the title in the SPMP.
\item Providing more details of the project organisation in the SPMP. 
\item Providing the explanation of the severity and likelihood of the risk management in the SPMP.
\end{itemize}

\vspace*{20pt}
\noindent  \textbf{Note:-} Next client meeting to be held on 11 November 2016 at Ingkarni Wardli 462,Computer Suite, Time: 10:40am .

\end{document}

