\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm
\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}

\begin{document}


\vspace*{15pt}
\begin{center}
\huge \bf Meeting Minutes
\end{center}

\section*{Chair: Yann Frizenschaf}
\section*{Secretory: Navdeep Singh}
\vspace*{10pt}

\section{Date and Time}
\begin{itemize}
\item Date: 13/09/2016
\item Time: 10:40am - 11:00am
\end{itemize}

\section{Apologies}
\begin{itemize}
\item Lili wu
\end{itemize}

\section{Present}
\begin{itemize}
\item Tao Zhang
\item Yi Lin
\item Yuan Liang

\item Zeqi Fu
\item Navdeep Singh
\item Yann Frizenschaf
\end{itemize}



\section{Summary }
Navdeep Singh summarized  the submitted  SPMP.

\begin{itemize}
\item SPMP draft completed. 
\item Navdeep Singh summarized  the submitted  SPMP.
\item No  need to submit the Milestone Form every time.
\item Milestone 1 Demo.
\item Some Discontinuities in the Boundary.
\item in   Document Type Declaration (DTD)  depth to color attribute  should be assigned by the team ,what color means should be assigned by the Team.
\item Clarify with David if obstacles are only points ,polygons ,etc

\end{itemize}




\section{Milestone 2 Freeze}
\begin{itemize}
\item Show Map Objects on a GUI
\item Show Basic  Automatic Movement of Robot.

\end{itemize}







\vspace*{20pt}
\noindent  \textbf{Note:-} Next client meeting to be held on 21 September 2016 at Ingkarni Wardli 462,Computer Suite, Time: 10:40am .


\end{document}
