\documentclass[11pt, a4paper]{article}

\usepackage{times}

\usepackage{ifthen}

\usepackage{amsmath}

\usepackage{amssymb}

\usepackage{graphicx}

\usepackage{setspace}



%%% page parameters

\oddsidemargin -0.5 cm

\evensidemargin -0.5 cm

\textwidth 15 cm

\topmargin -1.2 cm

\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize

\setlength{\parskip}{0pt}



\begin{document}



%%%mention the no, time, and venue of the meeting

\noindent The {\em first} Software Engineering Group (PG4) Project weekly meeting will be held in {\bf Room 462 (Ingkarni Wardli)} at {\bf 10:40am on Tuesday 16 August 2016}.



\vspace*{15pt}

\begin{center}

\huge \bf Agenda

\end{center}



%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.

\section*{Chair: Zeqi Fu}

\vspace*{10pt}



%%%if some students cannot make the meeting due to some reasons, their names should appear here.

\section{Apologies}

\begin{itemize}

\item none

\end{itemize}



%%%short presentation about the work of previous week or any milestone specified in the course.

\section{Presentation}

\begin{itemize}

\item Tao Zhang

\item Yi Lin

\item Yuan Liang

\item Lili Wu

\item Zeqi Fu

\item Navdeep Singh

\item Yann Frizenschaf

\end{itemize}



%%%any schedules for this meeting should go next, each with a separate section.

%%%for example, the first meeting is about requirement elicitation, like the following.

\section{Client}

The group shall present the items below with the client:



%%%if there are more subissues, make them as subsections.

\subsection{Requirements Summarise }

Zeqi Fu shall give a shortly summarise of the client's advanced requirements of the SeaFaults Mapping Robot. 



\begin{enumerate}

\item Feature: Movement,Mapping, and Version

\item Working Environment: plane

\item Operate Environment: GUI and automatically

\item Project Manager tools: Waterfall, Evolutionary Development, Component-based Development, and Agile Methods

\end{enumerate}



\subsection{Advanced requirements collection}

According to the advanced requirements team members ask some detailed questions to customers and teacher.

\begin{enumerate}

\item Movement

\begin{itemize}

\item Do we need make robot automatically detact the blocks and draw on screen or save it?

\item Can we control the robot as the core function, and advanced function be automatically finding shortest path?



\end{itemize}

\item Mapping

\begin{itemize}

\item What tools we can use in mapping progress?

\item Do we need emergency stop?



\end{itemize}



\item Project Manager tools

\begin{itemize}

\item Do they have prefer project manager tools to do the project?



\end{itemize}

\item Operations

\begin{itemize}

\item Are we required to design a UI for the operator? What are the required controls?

\end{itemize}

\end{enumerate}



\section{Group meeting summary}



\subsection{Three main function }



\begin{enumerate}

\item Version - robot color sensor

\item Mapping - distance, draw picture

\item Moving - moto drive, ultrasonic sensor

\end{enumerate}



\subsection{Things we made a decision}

\begin{enumerate}

\item Project manager:Yann Frizenschaf

\item We ganna decide which funcation can be core funcation, which part can be advaced function.





\item General progress update



\begin{itemize}

\item Tao Zhang already done the test of all the sensor, and can get the data range of each sensor.

\item After negotiation with gruop, we have regular meeting time,Monday and Thuesday.

\item Tao Zhang and Yi Lin focus on robot Movement, Yann Frizenschaf and Zeqi  Fu focus on Mapping, and Yuan Liang, Lili Wu, and Navdeep Singh will focus on Version part.

\end{itemize}



\item Presentation of draft requirements for client review

\begin{itemize}

\item we got RSR document draft and it list all the requirement, so this meeting we will discuss all the requirement

\end{itemize}

\end{enumerate}





 

%%%more issues should make it like the above one.

\section{Other Issues}



We can take mintues 

Yann Frizenschaf will confirm the next meeting



%%%finally, specifies time of next meeting

\vspace*{10pt}

\noindent Note: Next meeting to be held on 18 August 2016.





\end{document}
