\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm
\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}

\begin{document}


\vspace*{15pt}
\begin{center}
\huge \bf Meeting Minutes - PG 04
\end{center}

\section*{Chair: Lily Wu}
\vspace*{10pt}

\section{Date and Time}
\begin{itemize}
\item Date: 06/09/2016
\item Time: 10:40am - 11:00am
\end{itemize}

\section{Apologies}
\begin{itemize}
\item none
\end{itemize}

\section{Present}
\begin{itemize}
\item Tao Zhang
\item Yi Lin
\item Yuan Liang
\item Lili Wu
\item Zeqi Fu
\item Navdeep Singh
\item Yann Frizenschaf
\end{itemize}

\section{Secretary}
\begin{itemize}
\item Tao Zhang
\end{itemize}

\section{Summary }
Liang Yuan summarized the progress of the Draft SPMP:

\begin{itemize}
\item SPMP draft had been completed. 
\item Configuration management has been completed.
\item Double check Figure number has been added and linked to descriptions or not.
\end{itemize}

\section{Some roles are changed}

\begin{itemize}
\item Lili will be QA manager, be responsible for quality assurance including function testing and integrate testing.
\item Navdeep will be documentation manager, be responsible for keeping track of all the document is updated on time or not.
\item Tao will be assistant project manager, be responsible for keeping track the code part and help Yann to do some project management job.
\end{itemize}

\section{Gui presentation by Yann}

\begin{itemize}
\item Redesigned GUI is shown and updated buttons are operated by keyboard.
\item Better code encapsulation.
\item Merged prototype demo code into main project structure.
\end{itemize}

\section{Milestone freeze}
\begin{itemize}
\item Agreed with to show full manual control of robot (forward, reverse, 90 degree turns).
\item Agreed with to show Gui indication of position and orientation (map and numerical output).
\item Agreed with to show displaying current sensor (ultrasonic, color sensor, gyro) readings on Gui.
\end{itemize}

\section{SRS review}
\begin{itemize}
\item Put a before student id on cover.
\item Keep the revision history up to date and release version of draft should be 1.0. Put in the table who does what.
\item Reorder the wording may give a better explanation. For example, User Requirements (UR), Functional Requirements (FR) when first time introducing it. All prefixes should be checked.
\item Make the meaning of "While hardware considerations are touched on in the form of nonfunctional requirements" more clear.
\item Change "Description" to "Overall Description" on title of section2
\item Check the meaning of ‘Vision’. The ultrasonic sensor gives you distance data, but nothing like images.
\item Communications and Emergency operations are very important. Consider change the title ‘Auxiliary Systems’.
\item Seperate a subsection "constraints" from assumptions part.
\item Add ‘Status (implemented/unimplemented)’ and ‘Source’ for how we know th e requirements. If the requirement is no longer needed, make a note as well.
\item Define what automatic does in URC004.
\item Link requirements together if needed.
\item FRC002-004: What happens if the operator wants to move the robot outside the boundary manually?
\item FRC006: Looks like High priority.
\item FRC010: Everything should be finished within 20 mins, including demo.
\item FRC011: Decrease the error from 10cm to 7cm. Can also work out a more reasonable number after test.
\item FRE03: Where is FRE01 and 02? Why do we need Expedited Finish? What’s the source? From client meeting or project spec doc?
\item FRC0015-16: Maybe reorder the sentencing to make it clear. The work of Faultline Detection actually includes Depth Detection.
\item NRC001: work out a list of java version(java 1.8).
\item Add chapter for safety, quality assurance and user case.
\end{itemize}

\section{Wifi dongle}
\begin{itemize}
\item got a new Wifi dongle
\end{itemize}


\vspace*{10pt}
\noindent Note: Next client meeting to be held on 13 September 2016.


\end{document}
