\documentclass[11pt, a4paper]{article}

\usepackage{times}

\usepackage{ifthen}

\usepackage{amsmath}

\usepackage{amssymb}

\usepackage{graphicx}

\usepackage{setspace}



%%% page parameters

\oddsidemargin -0.5 cm

\evensidemargin -0.5 cm

\textwidth 15 cm

\topmargin -1.2 cm

\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize

\setlength{\parskip}{0pt}



\begin{document}



%%%mention the no, time, and venue of the meeting

\noindent The week 5 Software Engineering Group (PG4) Project weekly meeting will be held in {\bf Room 4.62 (Ingkarni Wardli)} at {\bf 10:40am on Tuesday 23rd August 2016}.



\vspace*{15pt}

\begin{center}

\huge \bf Agenda

\end{center}



%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.

\section*{Chair: Yann Frizenschaf}

\vspace*{10pt}



%%%if some students cannot make the meeting due to some reasons, their names should appear here.

\section{Apologies}

\begin{itemize}

\item none

\end{itemize}



%%%short presentation about the work of previous week or any milestone specified in the course.

\section{Present}

\begin{itemize}

\item Tao Zhang

\item Yi Lin

\item Yuan Liang

\item Lili Wu

\item Zeqi Fu

\item Navdeep Singh

\item Yann Frizenschaf

\end{itemize}



%%%any schedules for this meeting should go next, each with a separate section.

%%%for example, the first meeting is about requirement elicitation, like the following.

\section{Status update}

Yann Frizenschaf will provide a brief status update on the progress of the SFM project since the previous meeting, including:

\begin{enumerate}

\item Draft SRS completed after last's weeks requirements clarifications, ready for submission this week

\item Major class definitions and internal interfaces defined (formal UML diagram under construction)

\item Basic map data model designed

\item Sensor research conducted, more testing to follow

\item Agile project management methodology chosen, YouTrack tracking software selected (Sprint 1 finishes tomorrow)

\end{enumerate}

\section{SPMP clarification}

Navdeep will request clarification on the following points regarding the SPMP and deliverables:

\begin{enumerate}

\item The forum list two milestone "freezes" in weeks 7 and 8. Is it up to us or the client to determine what will be delivered at these milestones.

\item The major deliverables which will need to be specified in the SPMP are: User Manual. Final SRS, SPMP, SDD. Testing report. Are there any that we've missed?

\end{enumerate}

\section{Movement demo}

Yi Lin and Tao Zhang will clarify the following regarding the movement demo scheduled for the 29th of August:

\begin{enumerate}

\item What exactly would the client like to see from a GUI perspective? Our expectation is that we will deliver a GUI with basic manual movement controls for the robot, but no mapping functionality.

\item Following on from the above, our expectation is that we will demonstrate basic manual robot movement, with no autonomy yet.

\item When can we get access to a test survey area with the example colours and obstacles?

\end{enumerate}
 
 

%%%more issues should make it like the above one.

\section{Other Issues}

This week (according to the course forum) there is a YouTube review of the poster due. What are the requirements for this?

%%%finally, specifies time of next meeting

\vspace*{10pt}

\noindent The next meeting is to be held in {\bf Room 4.62 (Ingkarni Wardli)} at {\bf 10:40am on Tuesday 30th August 2016}.





\end{document}
